Recursive algorithms and branching for nonmaximal embeddings

### 2010-11-23 AffineLieAlgebras/InformalNotes/article.tex
More work on figures

There exist three level one fundamental weights of $\hat{A}_2$.
It is easy to see that the set $\Delta_{\afb}$ is empty and the subalgebra $\afb=0$.
It is convenient to choose the classical root for $\hat{A}_1$ to be
$\beta_1=\frac{1}{2}(\alpha_1+\alpha_2)$.

@@

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=135mm]{figure7.eps}
  \caption{The anomalous weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$.
  The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
by diamond when $\epsilon(w)=-1$. Simple roots of the classical subalgebra $A_2$ are
grey and the grey diagonal plane corresponds to the Cartan subalgebra of
the embedded algebra $\hat{A}_1$.}
  \label{fig:affine_A2_anom_point}
\end{figure}

@@

Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
$A_1 \rightarrow B_2$.
Since this embedding is regular and $x_e=1$, the subalgebra modules and the initial module are of the same level.
The set  of positive roots with zero projection
on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case
$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$.

Using the definition (\ref{fan-defined}) we obtain the fan
$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=0$.
The values of the sign function $s(\gamma)$ for
$ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ are presented in Figure \ref{fig:AffineB2A1Fan}.
We restricted the computation to the twelfth grade.
\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{figure10.eps}
  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$
  for $\hat{A_1}\rightarrow \hat{B_2}$ in the basis $\left\{\beta,\delta \right\}$. Values of  $s(\gamma)$ are shown for the
  weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{figure11.eps}
  \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$.
  The weights in the zero grade are the same as in Figure \ref{fig:B2_A1}.
  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by circles otherwise.
Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
of the embedded algebra $\hat{A}_1$.}
  \label{fig:affine_B2_anom_point}
\end{figure}

According to the algorithm \ref{sec:algorithm} we project the anomalous weights to
$P_{\hat{A_1}}$ and find the dimensions of the corresponding
$\afb$-modules $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$.
In the grade zero this is exactly the set of anomalous weights for the embedding of
the classical Lie algebra $A_1\rightarrow B_2$, to see this compare Figures \ref{fig:B2_A1}
and \ref{fig:AffineB2_A1_anom_proj}.
The result is presented in the Figure
\ref{fig:AffineB2_A1_anom_proj} up to the twelfth grade.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=120mm]{figure12.eps}
  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$. The dimensions of the corresponding $\afb=A_1$-modules with the signs $\epsilon(w)$ are shown.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

\begin{figure}[h!bt]
  \centering
  \includegraphics[width=120mm]{figure13.eps}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$.
  The boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
 are indicated by the black lines. The anomalous branching coefficients
 inside the main Weyl chamber are equal to the branching coefficients of the embedding $\hat{A_1}\rightarrow \hat{B_2}$.}
  \label{fig:AffineB2_A1_branching}
\end{figure}

>>>>

There exist three level one fundamental weights of $\hat{A}_2$.
It is easy to see that the set $\Delta_{\afb}$ is empty and the subalgebra $\afb=0$. Then ${\cal D}_{afb}=0$, $\hf_{\perp}$ is one-dimensional abelian subalgebra and the dimensions of $\tilde\afb=\afb\oplus \hf_{\perp}$ are equal to 1.
It is convenient to choose the classical root for $\hat{A}_1$ to be
$\beta=\frac{1}{2}(\alpha_1+\alpha_2)$.

@@

\begin{figure}[h!tb]
  \hspace*{-1.5cm}
  \includegraphics[width=180mm]{figure7-2.eps}
  \caption{The anomalous weights of the module $L_{\hat{A_2}}^{\omega_0}=L^{(0,0;1;0)}_{\hat{A_2}}$. In the classical cross-sections we use the orthogonal basis with the unit vector equal to $\alpha_1$.
  The weights $w (\omega_0+\rho)-\rho$ are marked by crosses when $\epsilon(w)=1$ and
by box when $\epsilon(w)=-1$. Simple roots of the classical subalgebra $A_2$ are
grey and the grey diagonal plane corresponds to the Cartan subalgebra of
the embedded algebra $\hat{A}_1$.}
  \label{fig:affine_A2_anom_point}
\end{figure}

@@

Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
$A_1 \rightarrow B_2$.
Since this embedding is regular and $x_e=1$, the subalgebra modules and the initial module are of the same level.
The set  of positive roots with zero projection
on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case
$\Delta^{+}_{\afb}=\left\{ \alpha_1 \right\}$. It is easy to see that $\hf_{\perp}$ is empty in this case and ${\cal D}_{\afb}=0$.

Using the definition (\ref{fan-defined}) we obtain the fan
$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$.
Notice that here the lowest weight  $\gamma_0$ of the fan  is zero and $s\left( \gamma_0 \right)=-1$.
The values of the sign function $s(\gamma)$ for
$ \gamma \in \Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ are presented in Figure \ref{fig:AffineB2A1Fan}.
We restricted the computation to the twelfth grade.
\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{figure10.eps}
  \caption{The fan $\Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$
  for $\hat{A_1}\rightarrow \hat{B_2}$ in the basis $\left\{\beta,\delta \right\}$. Values of  $s(\gamma)$ are shown for the
  weights $\gamma\in \Gamma_{\hat{A_1}\rightarrow \hat{B_2}}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{figure11.eps}
  \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$. The standard basis $\{e_1,e_2\}$ is used for the classical cross-section. 
  The weights in the zero grade are the same as in Figure \ref{fig:B2_A1}.
  The weights $w (\omega_1+\rho)-\rho$ are marked by crosses if $\epsilon(w)=1$ and by boxes otherwise.
Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
of the embedded algebra $\hat{A}_1$.}
  \label{fig:affine_B2_anom_point}
\end{figure}

According to the algorithm \ref{sec:algorithm} we project the anomalous weights to
$P_{\hat{A_1}}$ and find the dimensions of the corresponding
$\afb$-modules $L^{\pi_{\afb}(w(\mu+\rho))-\rho_{\afb}}_{\afb}$.
In the grade zero this is exactly the set of anomalous weights for the embedding of
the classical Lie algebra $A_1\rightarrow B_2$, to see this compare Figures \ref{fig:B2_A1}
and \ref{fig:AffineB2_A1_anom_proj}.
The result is presented in the Figure
\ref{fig:AffineB2_A1_anom_proj} up to the twelfth grade.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=120mm]{figure12.eps}
  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$. The basis $\{\beta,\delta\}$ is used. The dimensions of the corresponding $\afb=A_1$-modules with the signs $\epsilon(w)$ are shown.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

\begin{figure}[h!bt]
  \centering
  \includegraphics[width=120mm]{figure13.eps}
  \caption{Anomalous branching coefficients for $\hat{A_1}\rightarrow \hat{B_2}$. The basis $\{\beta,\delta\}$ is used.
  The boundaries  of the main Weyl chamber $\bar{C}_{\hat{A}_1}$
 are indicated by the black lines. The anomalous branching coefficients
 inside the main Weyl chamber are equal to the branching coefficients of the embedding $\hat{A_1}\rightarrow \hat{B_2}$.}
  \label{fig:AffineB2_A1_branching}
\end{figure}
